Untwisting the Tetrahelix (v0.4)

### 2017-02-11 doc/TetrahelixUntwist.tex
fixed bug with negative lambda values

\begin{align*}
r_{\lambda}  &=  \lambda (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
d_{\lambda} &=   \lambda (3 \sqrt{10} - 1) + 1 \\
\phi_{\lambda} &=  \lambda \rho_{bc}  + 0
\end{align*}
to create a formula that generates a continuum of tetrahedral structures:

@@

See if the continuum holds the short edge lengths at one perpetually.  Yes!!!

Create working toolkit for desin/exploration. Improve code that way, use white background, floor.

>>>>

\begin{align*}
r_{\lambda}  &=  \lvert \lambda \rvert (\frac{3 \sqrt{3}}{10}  - \sqrt{\frac{8}{27}}) + \sqrt{\frac{8}{27}}  \\
d_{\lambda} &=   \lvert \lambda \rvert (3 \sqrt{10} - 1) + 1 \\
\phi_{\lambda} &=  \lambda \rho_{bc}  + 0
\end{align*}
to create a formula that generates a continuum of tetrahedral structures:

@@

Understand why I can't control color completely!

Note that Lamba = 16 almost produces a 2-rail helicoid.

When abs(lambda) > 4, we seem to have marked differences in the parameters. Understand why this is and what is causing it.
(it is possible that positive and negative rho values behave very differently?

Note: Would be really nice to have the GUI show you all computed parameters.

Note: Distance is clearly lower on first computations..

Create working toolkit for desin/exploration.

Improve code that way, use white background, floor.

Figure out if I am computing something wrong.
